Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-05-20 doc/network.tex
a little more

The generation-interval-based approach to estimating the reproductive number assumes that an epidemic grows exponentially \citep{wallinga2007generation, park2019practical}.
In practice, heterogeneity in population structure can lead to subexponential growth \citep{chowell2016characterizing, viboud2016generalized}.

>>>>

The generation-interval-based approach to estimating the reproductive number assumes that an epidemic grows exponentially \citep{wallinga2007generation, park2019practical}.
In practice, heterogeneity in population structure can lead to subexponential growth \citep{szendroi2004polynomial, chowell2015western, chowell2016growing, chowell2016characterizing, kiskowski2016modeling, viboud2016generalized};
we therefore expect our simulations on an empirical network to be better characterized by subexponential growth models \citep{viboud2016generalized}.
However, our simulations suggest that the initial exponential growth assumption still provides a viable approach for estimating the reproductive number.
This conclusion is supported by \cite{chowell2015western} who found that epidemics can exhibit exponential growth patterns globally even if local epidemics may not.
